A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-09 doc/large_strain.tex
mention where the Roofline would go
more details on LIKWID

>>>>

% likwid-mpirun -np 10 -nperdomain S:10 -g MEM_DP -m $EXC
{\color{red}
Finally, we analyze the node-level performance of the two approaches using the Roofline model.
Memory bandwidth (MBytes/s) and the number of floating point operations per second (MFLOP/s) are measured using the \texttt{MEM\_DP} group of the LIKWID \cite{likwid} tool, version 4.2.1.
The measurements are done on a single socket of RRZE cluster by pinning all 10 MPI processes to this socket.
[DD]TODO: plot and discuss.
}
